\documentclass{resume}

\author{Alistair Pattison}
\title{
{\it (651) 706-6713}
\ | \
{\it pattisona@carleton.edu}
\ | \
\href{http://alipatti.com}{\it alipatti.com}
}

\usepackage[maxnames=100, giveninits=true]{biblatex}
\addbibresource{publications.bib}

\begin{document}

\maketitle

\section{Education}

\resumeitem{Bachelors of Arts, Mathematics \& Statistics}
{Carleton College}
{September 2020 -- June 2024}

\begin{itemize}
	\item 3.99 GPA,  minor in Digital Arts and Humanities.
	\item Captain of varsity track and field, all-conference honorable mention at 800m.
	\item Studied abroad at the University of Cambridge taking classes in computer science and history.
	\item Theses:
	      \textit{An Introduction to Analytic Number Theory} (math),
	      \textit{Live Win Probabilities in Soccer with RNNs} (stats).
\end{itemize}

% \resumeitem{Talented Youth Mathematics Program}
% {University of Minnesota}
% {2015 -- 2020}
%
% \begin{itemize}
% 	\item Completed selective high-school math program culminating in six semesters of set theory, vector calculus, linear algebra, and differential equations.
% \end{itemize}

\section{Work Experience}

\resumeitem{Research Assistant}
{University of Minnesota Privacy and Cryptography Group}
{September 2022 -- present}

\begin{itemize}
	\item Work with Professor Nicholas Hopper to develop privacy-preserving methods for reporting abuse and misinformation on encrypted messaging platforms.
	\item Write and benchmark proof-of-concept implementations in Python and Rust.
	\item Presented findings at a first-tier security conference in 2023. We plan to publish more results in 2024.
\end{itemize}

\resumeitem{Teaching Assistant}
{Carleton College}
{March 2021 -- present}

\begin{itemize}
	\item Tutor students, grade homework, and hold office hours for classes in the math and computer science departments.
	\item Classes:
	      Algorithms,
	      Artificial Intelligence,
	      Real Analysis I,
	      Abstract Algebra I,
	      Data Visualization,
	      Math Structures,
	      and Calculus II.
\end{itemize}

\resumeitem{Statistical Consultant}{Minnesota Department of Human Services}{September 2023 -- November 2023}

\begin{itemize}
	\item Worked with interdepartmental task force to help make Minnesota's government systems more inclusive of older adults.
	\item Analyzed American Community Survey data to identify demographic disparities in wealth, housing, and internet access.
	\item Created data visualizations and interactive dashboards for use by government employees and other consultants.
\end{itemize}

\resumeitem{The Food Guy}
{YMCA Camp Widjiwagan}
{June -- September 2021}

\begin{itemize}
	\item Oversaw the purchase and distribution of food for nearly 200 wilderness trips across the US and Canada.
	\item Managed a \$95,000 budget alongside two other employees and taught basic nutrition to kids aged 12 to 18.
	\item Lead a week-long canoeing trip with a program dedicated to making the outdoors more diverse and financially accessible.
\end{itemize}

\resumeitem{Dining Hall Worker}
{Carleton College}
{September 2020 -- March 2021}

% \resumeitem{Farm Hand}
% {Hansen Tree Farm}
% {2018 -- 2021}

% \resumeitem{Owner}
% {Pattison Lawn Care}
% {2015 -- 2020}

\smallskip

\section{Publications/Preprints}

\fullcite{cerberus}

\fullcite{threshold-reporting}

\fullcite{examplar}

% \fullcite{math-comps}

% \fullcite{stats-comps}

\section{Awards}

\newcommand{\award}[2]{\textbf{#1}, \textit{#2}}

\begin{itemize}[label={}, leftmargin=0em]
	\item \award{Phi Beta Kappa}{2023}
	      \quad \textit{(one of nine Junior-year inductees, roughly 2 percent of the class)}
	      % https://carleton-wp-production.s3.amazonaws.com/uploads/sites/287/2023/05/Carleton-Honors-Convocation-Program-2023.pdf
	\item \award{Dean's List}{2023, 2022, 2021}
	      \quad \textit{(awarded to top 10 percent of class by GPA)}
	\item \award{National Merit Scholarship}{2020}
	      \quad \textit{(awarded to roughly the top 1 percent of high-school seniors in the U.S.)}
\end{itemize}

\section{Projects}

\newcommand{\project}[2]{%
	\subsection{#1
		\hfill
		\normalfont \small \faicon{github}
		\href{http://github.com/alipatti/#2}{\textit{alipatti/#2}}
	}}

\project{Ole or Carl?}{ole-or-carl}

\begin{itemize}
	\item This project tests the validity of a long-standing stereotype that students from Northfield's two colleges look meaningfully different. If so, then a machine learning model should be able to tell them apart? Right?
	\item Uses a linear support-vector classifier on embeddings of student's faces taken from directory photos.
\end{itemize}

\project{Wordle Bot}{wordle-bot}

\begin{itemize}
	\item A Python and NumPy implementation, of 3Blue1Brown's information-theoretic Wordle bot, with a few improvements.
	\item Wins in $\sim 3.5$ moves on average.
\end{itemize}

\project{In Passing}{in-passing}

\begin{itemize}
	\item A visualization of passing and touch data from the 2022 FIFA Men's World Cup, built with d3.js.
\end{itemize}

\project{TODO.swift}{todo.swift}

\begin{itemize}
	\item A command line app to view and add to your Apple reminders, written in Swift.
	\item Directly updates Apple's iCloud database, so changes are reflected in the Reminders app across all your devices.
\end{itemize}

\project{An Introduction to Algebraic Number Theory}{math-comps}

\begin{itemize}
	\item A whirlwind introduction to number rings, number fields, the class group, and Dirichlet's unit theorem.
	\item Written as a senior thesis for the Carleton math department.
\end{itemize}

\project{OEIS.rs}{oeis.rs}

\begin{itemize}
	\item A terminal interface for the Online Encyclopedia of Integer Sequences, written in Rust.
	\item Provides interactive and non-interactive CLI.
\end{itemize}

\project{Carleton Course Classifier}{course-classifier}

\begin{itemize}
	\item A Tensorflow language model that predicts a course's department and number given its description.
	\item Achieves 64\% accuracy in a 54-class problem using a neural net and the Stanford GloVe embeddings.
\end{itemize}

\project{Smart Garage}{homekit-garage-door}

\begin{itemize}
	\item Uses an ESP32 microcontroller to integrate my parents' 40-year-old garage door opener with Apple HomeKit.
\end{itemize}


\section{Skills}

\textbf{Programming:} Python, R, JavaScript, \LaTeX, Rust, Java, SQL, git, Docker, Swift.

\textbf{Web Development:} Typescript, React, Next.js, Prisma.

\textbf{Data Science:} R (tidyverse, ggplot2), Python (NumPy, pandas, Matplotlib), SQL.

\textbf{Machine Learning:} TensorFlow, scikit-learn.

\textbf{Data Visualization:} ggplot2, matplotlib, d3.js.

\section{Coursework}

\textbf{Math}:
algebra, analysis, combinatorics, topology, analytic and algebraic number theory, representation theory, and Galois theory.

\textbf{Computer science}:
algorithms, data structures, cryptography, artificial intelligence, natural language processing, and quantum computing.

\textbf{Statistics}:
probability, regression, time-series analysis, machine learning, data science, and data visualization.

\section{Personal Interests}

Running, the Minnesota Timberwolves, the Premier League, backpacking, photography, playing the piano, Nordic skiing, Wii Mario Kart, tomfoolery.

\end{document}
